### 2021-02-12 treatise-context/4_simulation.tex
check chap 2, 3 LaTeX

From the simulation, DS outperforms other methods in most of the datasets.
In the scenario of low noise, \m {\T {\chi}} values of OMP and Lasso are close to DS.
But in the scenario of high noise, \m {\T {\chi}} values of OMP and Lasso blow up quickly.

It is intuitive that when \m {N_{B,t} /N_{B,r}} is smaller, \m {\T {\chi}} is smaller, because we have a higher sample rate.
As \m {N_{B,t} /N_{B,r}} increase for given \m {\s}, the DS line improves more significantly, and \m {\T {\chi}} falls nearly always below \m {0} dB for \m {N_{B,t} > N_{B,r}} case.

The design of sample matrix seems to have a lot to do with the performance of OMP.
In Lee, Gil, and Lee \cite [LGL16], a high-complexity nonconvex program is used to design the sensing matrix, while we have here a low-complexity, random generation of beamforming matrices.
It may also have something to do with the distribution of angles of departure and arrival.

The performance of Lasso also fails mostly for low noise.
Recall from above that \m {\g} (or \m {\l}) is crucial to the performance, but cannot be obtained in advance.
Thus, for sake of comparison, we set the same threshold (and BPDN) for Lasso and DS.
We should not however there may be other values of \m {\g} (or \m {\l}) for which DS and Lasso are both better.

For Moore Penrose pseudoinverse, \m {\T {\chi}} increases tremendously as \m {\s} decreases, and the trend is steady and may serve as a upper bound.

For DS itself, \m {\T {\chi}} decreases as \m {\s} increases, which is expected, but \m {\T {\chi}} does not go down indefinitely.
The values of threshold of DS \m {\g_{\Rm {DS}}} are chosen within the order of magnitude of \m {\s}.
It may have been that the iteration stabilizes much earlier than is constrained by maximum iteration number.

@@

We see that \m {\RB {\M {P} ^\Adj \V {z}} _{\SB {j}}} follows complex standard normal distribution.
If we agree that, for high probability,
%
\DispNum {O:j:sO:O1} {
\NC \MS {O} \SB {\VNm {\M {P} ^\Adj \V {z}} _{\SB {j}}}
= \NC \s \MS {O} \RB {1} \NR
}
Then we have
%
\DispNum {C:S:ON:H6} {
\NC C_{\Rm {DS}}
=\NC \MS {O} \SB {N_{H}^6} \NR
}

>>>>

From the simulation, DS outperforms other methods in most of the datasets.
With low noise, \m {\T {\chi} _{\Rm {DS}} \approx \T {\chi} _{\Rm {OMP}} \approx \T {\chi} _{\Rm {Lasso}} \approx \T {\chi} _{\Rm {LS}}}.
But with high noise, \m {\T {\chi} _{\Rm {OMP}}, \T {\chi} _{\Rm {Lasso}}, \T {\chi} _{\Rm {LS}}} blow up quickly,
and it is usually true that \m {\T {\chi} _{\Rm {DS}} \leq \T {\chi} _{\Rm {OMP}} \leq \T {\chi} _{\Rm {Lasso}} \leq \T {\chi} _{\Rm {LS}}}.

For OMP, in Lee, Gil, and Lee \cite [LGL16], a high-complexity nonconvex program is used to design the sensing matrix, while we have here a low-complexity, random generation of beamforming matrices.
We keep in mind that a different design of sensing matrix, or a distribution of angles, will affect the performance of OMP.

For Lasso, \m {\g} (or \m {\l}) is also crucial to the performance, but cannot be obtained in advance.
Thus, for sake of comparison, we set the same threshold (and BPDN) for Lasso and DS.
Still, there may be other values of \m {\g} (or \m {\l}) for which DS and Lasso are both better.

For DS itself, first, \m {\T {\chi} _{\Rm {DS}}} certainly decreases as \m {\s} increases, but it does not decrease indefinitely.
Second, \m {\T {\chi} _{\Rm {DS}}} decreases as \m {N_H} increases.
Third, when \m {N_{B,t} /N_{B,r}} is smaller, \m {\T {\chi} _{\Rm {DS}}} is smaller, because we have a higher sample rate.
As \m {N_{B,t} /N_{B,r}} increase for given \m {\s}, \m {\T {\chi} _{\Rm {DS}}} improves more significantly.

@@

We see that \m {\RB {\M {P} ^\Adj \V {z}} _{\SB {j}}} follows complex standard normal distribution.
If we agree that, for high probability,
%
\DispNum {O:j:sO:O1} {
\NC \MS {O} \SB {\VNm {\M {P} ^\Adj \V {z}} _{\SB {j}}}
= \NC \s N_H^2 \MS {O} \RB {1} \NR
}
Then we have
%
\DispNum {C:S:ON:H6} {
\NC C_{\Rm {DS}}
=\NC \MS {O} \SB {N_{H}^6} \NR
}

### 2021-02-12 treatise-pdflatex/4_simulation.tex
check chap 2, 3 LaTeX

In the assorted plots, DS steadily outperforms other methods.
From lowest to highest error, it usually goes like this: DS, LS, Lasso, OMP.

The performance of OMP appears to be poor.
In most cases, the estimation fails, and we have \m {\tilde {\chi}} close to the unity.
Varying thresholds of OMP, namely \m {\h_{\mathrm {OMP}}}, does not give different result.

A crucial reason might be that Lee, Gil, and Lee \cite {LGL16} proposed a high-complexity nonconvex program for the beamformers, which they gave approximation, and we have here a low-complexity, randomly-generated beamformers.
It may also have something to do with the distribution of angles of departure and arrival;
their distribution lies within a cluster of standard deviation 15 degrees, and in ours, they are uniform on the unit circle.
It remains to see how OMP and DS compare, if done according to their procedure.

The performance of Lasso also fails mostly, and \m {\tilde {\chi}} even increase as \m {\s} decreases, which is strange.

For Moore Penrose pseudoinverse, \m {\tilde {\chi}} decreases steadily as \m {\s} decreases.

For DS itself, \m {\tilde {\chi}} decreases as \m {\s} increases, which is expected, but \m {\tilde {\chi}} does not go down indefinitely, even for very low \m {\s}.
The values of threshold of DS \m {\g_{\mathrm {DS}}} are chosen within the order of magnitude of \m {\s}.
For high signal level, \m {\g_{\mathrm {DS}}} does not affect much, but for low signal level a greater value may be more effective.
It may have been that the iteration stabilizes much earlier than is constrained by maximum iteration number.

@@

We are not sure either why \m {\tilde {\chi}} is an overestimation of \m {\chi} by several orders of magnitude.
A possible explanation is that the non-sparsity of \m {\V {g}} undermines the analysis in chapter 3, despite our attempts to account for that effect.

@@

We see that \m {\RB {\M {P} ^\dagger \V {z}} _{\SB {j}}} observes complex standard normal distribution.
If we agree that, for high probability,
%
\DispNum {O:j:sO:O1} {
\mathcal {O} \SB {\VNm {\M {P} ^\dagger \V {z}} _{\SB {j}}}
= \s \mathcal {O} \RB {1} 
}
Then we simply have
%
\DispNum {C:S:ON:H6} {
C_{\mathrm {DS}}
=\mathcal {O} \SB {N_{H}^6} 
}

>>>>

From the simulation, DS outperforms other methods in most of the datasets.
With low noise, \m {\tilde {\chi} _{\mathrm {DS}} \approx \tilde {\chi} _{\mathrm {OMP}} \approx \tilde {\chi} _{\mathrm {Lasso}} \approx \tilde {\chi} _{\mathrm {LS}}}.
But with high noise, \m {\tilde {\chi} _{\mathrm {OMP}}, \tilde {\chi} _{\mathrm {Lasso}}, \tilde {\chi} _{\mathrm {LS}}} blow up quickly,
and it is usually true that \m {\tilde {\chi} _{\mathrm {DS}} \leq \tilde {\chi} _{\mathrm {OMP}} \leq \tilde {\chi} _{\mathrm {Lasso}} \leq \tilde {\chi} _{\mathrm {LS}}}.

For OMP, in Lee, Gil, and Lee \cite [LGL16], a high-complexity nonconvex program is used to design the sensing matrix, while we have here a low-complexity, random generation of beamforming matrices.
We keep in mind that a different design of sensing matrix, or a distribution of angles, will affect the performance of OMP.

For Lasso, \m {\g} (or \m {\l}) is also crucial to the performance, but cannot be obtained in advance.
Thus, for sake of comparison, we set the same threshold (and BPDN) for Lasso and DS.
Still, there may be other values of \m {\g} (or \m {\l}) for which DS and Lasso are both better.

For DS itself, first, \m {\tilde {\chi} _{\mathrm {DS}}} certainly decreases as \m {\s} increases, but it does not decrease indefinitely.
Second, \m {\tilde {\chi} _{\mathrm {DS}}} decreases as \m {N_H} increases.
Third, when \m {N_{B,t} /N_{B,r}} is smaller, \m {\tilde {\chi} _{\mathrm {DS}}} is smaller, because we have a higher sample rate.
As \m {N_{B,t} /N_{B,r}} increase for given \m {\s}, \m {\tilde {\chi} _{\mathrm {DS}}} improves more significantly.

@@

\m {\tilde {\chi}} is not shown in the figure, because the big O bound is much larger than \m {\chi}.
It is possible that the nonsparsity of \m {\V {g}} undermines the analysis in chapter 3, despite our attempts to account for that effect.
It is curious to see whether for very large \m {N_H}, whether \m {\tilde {\chi}} and \m {\tilde {\chi}} will be asymptotically close.

@@

We see that \m {\RB {\M {P} ^\dagger \V {z}} _{\SB {j}}} observes complex standard normal distribution.
If we agree that, for high probability,
%
\DispNum {O:j:sO:O1} {
\mathcal {O} \SB {\VNm {\M {P} ^\dagger \V {z}} _{\SB {j}}}
= \s N_H^2 \mathcal {O} \RB {1} 
}
Then we simply have
%
\DispNum {C:S:ON:H6} {
C_{\mathrm {DS}}
=\mathcal {O} \SB {N_{H}^6} 
}
